---
title: "Visitors to Kenya between 1991-2014"
author: "Daniel Obare"
date: "1/9/2020"
output: 
  html_document:
    keep_md: yes
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
      smooth_scroll: yes

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE, 
                      message = FALSE)
```

# Package Library

## Load desired package libraries

```{r packages}
require(dplyr)
require(tidyr)
require(magrittr)
require(ggplot2)
require(ggthemes)
theme_set(theme_classic())
require(kableExtra)
require(lubridate)
load(file = "visitor.Rdata")
```

## The raw data itself

```{r vis data}
attach(Visitors_to_Kenya_between1991_to_2014_For_Developers)
Visitors_to_Kenya_between1991_to_2014_For_Developers %>% kable() %>% kable_styling() %>% 
  scroll_box(width = "100%", height = "300px")
```

## Summary Statistics and Structure

We take a look at the **Summary statistics** and it's **Structure**

```{r dataset}
vis = Visitors_to_Kenya_between1991_to_2014_For_Developers
attach(vis)
vis %>% str()
vis %>% summary()
```

# Arrivals or Departures

## Structure

```{r structure}
vis$Arrival_or_Departure = as.factor(vis$Arrival_or_Departure)
vis$Arrival_or_Departure %>% summary()
```
## visual of Arrivals or Departures

```{r plot}
vis %>% ggplot(aes(Arrival_or_Departure))+
  geom_bar()+
  ggtitle("Arrivals or Departures")
```

# Date_End_of_Quater

## Date Formatting

The Quarter ends at **mid-night** that is 12:00:00 AM 

```{r date formatting}
vis$Date_End_of_Quater = vis$Date_End_of_Quater %>%  mdy_hms()
vis$Date_End_of_Quater %>% summary()
```

# Number of Visitors to Kenya

## Check for any errors and data wrangling

```{r}
summary(vis$No_of_Visitors_to_Kenya)
vis %>% is.na() %>% any()

x <- vis %>% select(-OBJECTID) %>% mutate(Year_Text = factor(Year_Text)) %>% 
  mutate(Visitors_by_Purpose = factor(Visitors_by_Purpose)) %>% 
  mutate(Period_Quater = factor(Period_Quater)) %>% mutate(Results_Status = factor(Results_Status)) %>% 
  group_by(No_of_Visitors_to_Kenya) %>% 
  janitor::clean_names()
```

## visual of the number of visitors to Kenya

```{r}
normalize <- function(x){
  return((x-min(x))/(max(x)-min(x)))
}

x %>% ggplot(aes(visitors_by_purpose, normalize(no_of_visitors_to_kenya)))+
  geom_bar(stat = "identity", fill = "blue")+
  coord_flip()+
  xlab("visito by purpose")+
  ylab("number of visitors")+
  ggtitle("Number of visitors by Purpose")

x %>% ggplot(aes(visitors_by_purpose, normalize(no_of_visitors_to_kenya)))+
  geom_bar(stat = "identity", fill = "blue")+
  coord_flip()+
  xlab("visito by purpose")+
  ylab("number of visitors")+
  ggtitle("Number of visitors by Purpose")+
  facet_wrap(~period_quater)

x %>% ggplot(aes(visitors_by_purpose, normalize(no_of_visitors_to_kenya)))+
  geom_bar(stat = "identity", fill = "blue")+
  coord_flip()+
  xlab("visito by purpose")+
  ylab("number of visitors")+
  ggtitle("Number of visitors by Purpose")+
  facet_wrap(~results_status)

```




